Age-related changes in plant growth and traits

### 2015-05-05 results_RAschedules.Rmd
starting to summarize results deleted some outdates, duplicate scripts few thoughts about shoot extension - to be improved upon

#RV curves
These are mostly reasonably nice - of course need to fit quadratic curve to these and haven't figured out how to do it correctly

```{r, echo=FALSE,message=FALSE}
plot(ReproInv~FinalWeight, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

#RV curves (by age)
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~age, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

@@

```{r, echo=FALSE,message=FALSE}
plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

plot(RGR~RA, data=subset(SummaryInd,RA>0), log="xy", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
mod <- lm(log(GrowthInv)~asin(sqrt(RA)), data=subset(SummaryInd,RA>0))
summary(mod)
plot(mod)

>>>>

#RV curves
###Classic RV curves - reproductive investment versus weight
- These are mostly reasonably nice - of course need to fit quadratic curve to these and haven't figured out how to do it correctly  
- The plot that includes all species shows that *once* a given species has ramped up reproduction, the log-log plot of reproductive investment vs final weight is nearly linear across all species; in other words, to first order, all species allocate the same amount to reproduction relative to their weight.
- However, it is important to note that species early in their reproductive trajectory do not follow this pattern
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~FinalWeight, SummaryInd, log="xy",col=col.spp[as.factor(species)],pch=16)
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

###RV curves (by age)
```{r, echo=FALSE,message=FALSE}
plot(ReproInv~age, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend(15,5000,legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

###RV curves (by proportion max H)
- In a sense, by using proportion max H, these figures are showing the proportion of total growth the plant undergoes before starting reproduction
- You could also plot against "PropMaxWeight", the proportion of the heaviest individual of that species. The two measures look "best" for different species
```{r, echo=FALSE,message=FALSE}
plot((PropMaxRepro+.1)~(PropH), SummaryInd, log="y",col=col.spp[as.factor(species)],pch=16,xlim=c(4e-03,1))
legend("topleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

yvar <- "ReproInv"
xvar <- "PropH"

data <- SummaryInd
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]+1) ~  (x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, 
                    main=spp, log="y", xlab=xvar, ylab=yvar)

@@

```{r, echo=FALSE,message=FALSE}
plot(RA~RGR, SummaryInd, log="xy", col=col.spp[as.factor(species)],pch=16)
legend("bottomleft",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")

@@

plot(RGR~RA, data=subset(SummaryInd,RA>0), log="xy", col=col.spp[as.factor(species)],pch=16)
legend("topright",legend=names(labels.spp),col=col.spp,pch=16, cex=.8,bty="n")
mod <- lm(log(GrowthInv)~asin(sqrt(RA))*species, data=subset(SummaryInd,RA>0))
summary(mod)
anova(mod)
plot(mod)

### 2015-05-05 results_growth.Rmd
starting to summarize results deleted some outdates, duplicate scripts few thoughts about shoot extension - to be improved upon

>>>>

  abline(lmfits[[spp]])
}
```
###Diameter increase in shoots vs. whole plant
- The slope of the relationship lessens with age  
- There is quite a bit of noise in the relationship  
- However, in many cases, older plants show less of a change in shoot diameter for a given change in basal diameter; the opposite pattern as is predicted if ever fewer shoots are sustaining growth  
- Instead, each shoot matters ever less to the overall increase in basal area in larger plants
- NOTE: Plots not correct right now - wrong number of points in some and definitely wrong coloring by age
```{r, echo=FALSE,message=FALSE}
plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.spp[as.factor(species)], pch=16)
abline(0,1)

mod <- lm (change_shoot_diam ~ change_basal_diam*age,data=subset(SummaryInd, age>1.4))
summary(mod)
anova(mod)

plot((change_shoot_diam/100) ~ change_basal_diam,data=subset(SummaryInd, age>1.4), log="xy",col=col.age2[as.factor(age)], pch=16)
abline(0,1)
legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")

plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.spp[as.factor(species)], pch=1)

plot((change_shoot_area/10000) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=16,ylim=c(0.01,500),cex=.7)
points((change_basal_area) ~ FinalBasalDiamAv,data=subset(SummaryInd), log="xy",col=col.age[as.factor(age)], pch=1)

yvar <- "change_shoot_diam"
xvar <- "change_basal_diam"

data <- subset(SummaryInd)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log(x[[yvar]]) ~  log(x[[xvar]])))
results <- summarise_all_fits(lmfits)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar, log="xy", col=col.age[as.factor(SummaryInd$age)],
                    main=spp, xlab=xvar, ylab=yvar)
  legend("bottomright",col=col.age, labels.age, pch=16, cex=1, bty="n")
}
```
